---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
```

# codeexplode

```{r advert, warning=F, echo=F}
library(ggstamp)
magick::image_read("https://images.unsplash.com/photo-1557801200-9a8d901ded2a?ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&ixlib=rb-1.2.1&auto=format&fit=crop&w=687&q=80") %>%
  magick::image_write(format = "png") %>%
  ggbackdrop(png = .) +
  stamp_label(label = "pipelines",
              label.size = 1.5,
             x = 20, y = 10, size = 12) +
  stamp_arrow(x = 27, y = 16, size = 4, 
              headlength = .1,
              type = "closed",angle = 20,
              xend = 48, yend = 40,
              color = "slateblue") + 
  stamp_label(label = "flipbook",
             x = 65, y = 50, label.size = 2,
             size = 22, color = "goldenrod3") +
  stamp_curve(y = 35+10, 
              xend = 30:20 + 60, 
              yend = 40:50 + 10,
              curvature = .1, 
              x = 44,
              alpha = .1) + 
  stamp_polygon(x0 = 70, y0 = 20, 
                radius = 20,
                fill = "brown",
                alpha = .7,
                size = 1.5,
                color = "brown") + 
  stamp_label(label = "{codeexplode}",
              fontface = "bold",
              x = 70, y = 20,
              size = 12, 
              color = "slateblue",
              label.size = 2
              ) + 
  stamp_text(x = 99, angle = 90, 
             y = 20,
             label = "photo credit, Erwan Hesry",
             size = 3,
             color = "grey70") +
  theme_void()
```

<!-- badges: start -->
<!-- badges: end -->


flipbooks -- go-at-your-own-pace, code and output animations -- have up to this point been *crafted* for education and demonstration purposes.  


The flipbook format doesn't make much sense for getting actual work done.  It is inefficient.  We repeat steps (step 1, steps 1-2, steps 1-3) to create the animation.  

However, code that isn't developed with a flipbook end presentation in mind might also might be easier to consume in the flipbook format.  It might be transformed into a educational or code-review tool on occasion.  

---

The goal of codeexplode is to take a .Rmd input (maybe a .R file later), and convert this to a flipbook product.

This is done by creating a new .Rmd file from a source .Rmd file where 

1) the original yaml is replaced with a flipbook-ready yaml (output to xaringan) 
2) flipbookr::chunk_reveal() is paired with each existing code chunks to 'explode' them; the original source code chunks are reset to include = FALSE.

---

Right now, {codeexplode} is not that clever.  It work best for auto-type reveal, where code is written in a sequential way and you would be able to see outputs as you go. (i.e. right assignment).

---

## Installation

And the development version from [GitHub](https://github.com/) with `devtools::install_github("EvaMaeRey/codeexplode")`

---


## Code that plays nice with codeexplode

The following code works well because it is piped, and most pause points (where parentheses are balanced at the end of a line) will produce an output.

```{r cars}
summary(cars) ->
  summary_cars

library(ggplot2) 
cars %>% 
  ggplot() + 
  aes(x = speed, y = dist) + 
  geom_point(size = 4) + 
  aes(color = speed) + 
  scale_color_viridis_c()

```

---

# codeexplode in action

Now let's also look at what codeexplode does with this .Rmd.  

``` r
codeexplode::rmd_code_explode("README.Rmd",
  rmd_output = "docs/readme_exploded.Rmd")
```  

I rendered the exploded and rendered the .Rmd outside this file, because if felt to mind-bendy to do here.  The resultant flipbook (.html) is shown here.

---

<div style="position:relative;padding-top:56.25%;">

<iframe src="https://evamaerey.github.io/codeexplode/readme_exploded.html" frameborder="2" webkitallowfullscreen mozallowfullscreen allowfullscreen style="position:absolute;top:0;left:0;width:100%;height:100%;" allowtransparency="true">
</iframe>

</div>




