---
title: "Exploded code"
subtitle: "Using flipbookr and xaringan"
author: "Me"
output:
  xaringan::moon_reader:
    lib_dir: libs
    css: [default, hygge, ninjutsu]
    nature:
      ratio: 16:9
      highlightStyle: github
      highlightLines: true
      countIncrementalSlides: false
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

---

`r flipbookr::chunk_reveal("setup")`

---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

library(tidyverse)
```

# codeexplode

---

`r flipbookr::chunk_reveal("advert")`

---

```{r advert, warning=F, echo=F, include = FALSE}
library(ggstamp)
magick::image_read("https://images.unsplash.com/photo-1614176710432-81bdf52f120f?ixid=MnwxMjA3fDB8MHxwaG90by1wYWdlfHx8fGVufDB8fHx8&ixlib=rb-1.2.1&auto=format&fit=crop&w=751&q=80") %>%
  magick::image_write(format = "png") %>%
  ggbackdrop(png = .) +
  stamp_label(label = "pipelines",
              label.size = 1.5,
             x = 20, y = 10, size = 9) +
  stamp_arrow(x = 27, y = 16, size = 4, 
              headlength = .1,
              type = "closed",angle = 20,
              xend = 48, yend = 40,
              color = "slateblue") + 
  stamp_text(label = "flipbooks",
             x = 65, y = 50, 
             size = 17) +
  stamp_curve(y = 35+10, 
              xend = 30:20 + 60, 
              yend = 40:50 + 10,
              curvature = .1, 
              x = 44,
              alpha = .1) + 
  stamp_polygon(x0 = 80, y0 = 20, 
                radius = 14,
                fill = "brown",
                alpha = .7,
                size = 1.5,
                color = "brown") + 
  stamp_text(label = "{codeexplode}",
               fontface = "bold",
               x = 80, y = 20,
               size = 5, 
               color = "oldlace") + 
  stamp_text(x = 99, angle = 90, 
             y = 20,
             label = "photo credit, Daniele Levis Pelusi",
             size = 3,
             color = "grey70") +
  theme_void()
```

<!-- badges: start -->
<!-- badges: end -->


flipbooks -- go-at-your-own-pace, code and output animations -- have up to this point been *crafted* for education and demonstration purposes.  


The flipbook format doesn't make much sense for getting actual work done.  It is inefficient.  We repeat steps (step 1, steps 1-2, steps 1-3) to create the animation.  

However, code that isn't developed with a flipbook end presentation in mind might also might be easier to consume in the flipbook format.  It might be transformed into a educational or code-review tool on occasion.  

---

Right now, {codeexplode} is not that clever.  It work best for auto-type reveal, where code is written in a sequential way and you would be able to see outputs as you go. (i.e. right assignment).

---

## Installation

And the development version from [GitHub](https://github.com/) with `devtools::install_github("EvaMaeRey/codeexplode")`

---


## Code that plays nice with codeexplode

The following code works well because it is piped, and most pause points (where parentheses are balanced at the end of a line) will produce an output

---

`r flipbookr::chunk_reveal("cars")`

---

```{r cars, include = FALSE}
summary(cars) ->
  summary_cars

library(ggplot2) 
cars %>% 
  ggplot() + 
  aes(x = speed, y = dist) + 
  geom_point(size = 4) + 
  aes(color = speed) + 
  scale_color_viridis_c()

```

---

# codeexplode in action

Now let's also look at what codeexplode does with this .Rmd.  I rendered the exploded .Rmd outside this file, because if felt to mind-bendy to do here.  The resultant flipbook (.html) is hosted on github, and we want to include it.

---

`r flipbookr::chunk_reveal("exploding_readme")`

---

```{r exploding_readme, include = FALSE}
"https://evamaerey.github.io/codeexplode/readme_exploded.html" %>% 
knitr::include_url()
```


